---
title: "DA & Discounting - Exploratory Analyses"
author: "Jaime J. Castrellon, Kendra L. Seaman, Jennifer L. Crawford, Jacob S. Young, Christopher T. Smith, Linh C. Dang, Ming Hsu, Ronald L. Cowan, David H. Zald, Gregory R. Samanez-Larkin"
date: "September 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Individual differences in dopamine are associated with reward discounting in clinical groups but not in healthy adults - Exploratory analyses {.tabset}


###Build, packages, & data
Session info
```{r}
devtools::session_info()
```
Packages
```{r results='hide', message=FALSE, warning=FALSE}
library(ggplot2)
library(ggpubr)
library(dplyr)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(sjstats)
```
Load data
```{r}
data = read.csv(file="./study01_data_exploratory_analyses.csv",header=TRUE, sep=",")
```
Set seed (for reproducible results) 
```{r}
set.seed(1000)
```
Get discounting measures (time, probability, effort)
```{r}
varlist <- names(data)[c(63,65,66,68,69,71)]
print(varlist)
```


###Main effects of age, sex, study, and interactions of age and study
Examine main effects of age, sex, study, and dopamine on discounting and interactions of age and dopamine & study and dopamine where possible

####Midbrain
```{r}
midbrain <- lapply(varlist, function(x) {
    lm(substitute(i ~ age + male + study2 + study3 + midbrain + agexmidbrain + s2xmidbrain + s3xmidbrain, list(i = as.name(x))), data = data)
})

sjt.glm(midbrain,digits.est = 5, digits.ci = 5,p.numeric = TRUE, digits.p=5, emph.p=TRUE, exp.coef=FALSE)
```

####Ventral Striatum
```{r}
accumbens_pvc <- lapply(varlist, function(x) {
    lm(substitute(i ~ age + male + study2 + accumbens_pvc + agexnacc + s2xnacc, list(i = as.name(x))), data = data)
})

sjt.glm(accumbens_pvc,digits.est = 5, digits.ci = 5,p.numeric = TRUE, digits.p=5, emph.p=TRUE, exp.coef=FALSE)
```

####Caudate

```{r}
caudate_pvc <- lapply(varlist, function(x) {
    lm(substitute(i ~ age + male + study2 + caudate_pvc + agexcaud + s2xcaud, list(i = as.name(x))), data = data)
})

sjt.glm(caudate_pvc,digits.est = 5, digits.ci = 5,p.numeric = TRUE, digits.p=5, emph.p=TRUE, exp.coef=FALSE)
```

####Putamen
```{r}
putamen_pvc <- lapply(varlist, function(x) {
    lm(substitute(i ~ age + male + study2 + putamen_pvc + agexput + s2xput, list(i = as.name(x))), data = data)
})

sjt.glm(putamen_pvc,digits.est = 5, digits.ci = 5,p.numeric = TRUE, digits.p=5, emph.p=TRUE, exp.coef=FALSE)
```

####Amygdala

```{r}
amygdala_pvc <- lapply(varlist, function(x) {
    lm(substitute(i ~ age + male + study2 + study3 + amygdala_pvc + agexamyg + s2xamyg + s3xamyg, list(i = as.name(x))), data = data)
})

sjt.glm(amygdala_pvc,digits.est = 5, digits.ci = 5,p.numeric = TRUE, digits.p=5, emph.p=TRUE, exp.coef=FALSE)
```

####Hippocampus

```{r}
hippocampus_pvc <- lapply(varlist, function(x) {
    lm(substitute(i ~ age + male + study2 + study3 + hippocampus_pvc + agexhipp + s2xhipp + s3xhipp, list(i = as.name(x))), data = data)
})

sjt.glm(hippocampus_pvc,digits.est = 5, digits.ci = 5,p.numeric = TRUE, digits.p=5, emph.p=TRUE, exp.coef=FALSE)
```

####Thalamus

```{r}
thalamus_pvc <- lapply(varlist, function(x) {
    lm(substitute(i ~ age + male + study2 + study3 + thalamus_pvc + agexthal + s2xthal + s3xthal, list(i = as.name(x))), data = data)
})

sjt.glm(thalamus_pvc,digits.est = 5, digits.ci = 5,p.numeric = TRUE, digits.p=5, emph.p=TRUE, exp.coef=FALSE)
```

####ACC

```{r}
acc_pvc <- lapply(varlist, function(x) {
    lm(substitute(i ~ age + male + study2 + study3 + acc_pvc + agexacc + s2xacc + s3xacc, list(i = as.name(x))), data = data)
})

sjt.glm(acc_pvc,digits.est = 5, digits.ci = 5,p.numeric = TRUE, digits.p=5, emph.p=TRUE, exp.coef=FALSE)
```

####Insula

```{r}
insula_pvc <- lapply(varlist, function(x) {
    lm(substitute(i ~ age + male + study2 + study3 + insula_pvc + agexins + s2xins + s3xins, list(i = as.name(x))), data = data)
})

sjt.glm(insula_pvc,digits.est = 5, digits.ci = 5,p.numeric = TRUE, digits.p=5, emph.p=TRUE, exp.coef=FALSE)
```

###Follow-up age interaction plots

Tertiary split age variable for visualization
```{r}
data$age_tertiary_split <- ntile(data$age, 3)
data$age_tertiary_split <- factor(data$age_tertiary_split, labels = c("YA", "MA", "OA"))
```

Age group descriptive stats
```{r}
desc_statby(data, "age", grps = "age_tertiary_split", ci = 0.95)
```

Plot ages per group
```{r}
 p <- ggboxplot(data, x = "age_tertiary_split", y = "age",
      color = "age_tertiary_split", palette ="jco", legend.title = "Age Group",
      xlab = "Age Group", ylab = "Age", add = "jitter", shape = "age_tertiary_split")
 p
```

Mean age per age group
```{r}
grpmean(data, age, age_tertiary_split)
```

####Age * Midbrain Interaction: Effort Discounting
Chose Low Effort
```{r}
midbrain_effort <- ggscatter(data, x = "midbrain", y = "choseloeffort",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(0.5,2), ylim=c(0,1),                             #x,y bounds
  xlab = "Midbrain DRD2 BPND", ylab = "prop(Low Effort)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 1.5)  # Add correlation coefficient
midbrain_effort
```

Effort (Ln(k+1))
```{r}
midbrain_effort <- ggscatter(data, x = "midbrain", y = "effort_ln_k1",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(0.5,2), ylim=c(0,3),                             #x,y bounds
  xlab = "Midbrain DRD2 BPND", ylab = "Effort (Ln(k+1))",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 1.75)  # Add correlation coefficient
midbrain_effort
```

####Age * Ventral Striatum Interaction: Time Discounting
Chose Sooner
```{r}
vstr_time <- ggscatter(data, x = "accumbens_pvc", y = "chosesnr",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(10,60), ylim=c(0,1),                             #x,y bounds
  xlab = "Ventral Striatum DRD2 BPND", ylab = "prop(Sooner)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 14)  # Add correlation coefficient
vstr_time
```

####Age * Ventral Striatum Interaction: Effort Discounting
Chose Low Effort
```{r}
vstr_effort <- ggscatter(data, x = "accumbens_pvc", y = "choseloeffort",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(10,60), ylim=c(0,1),                             #x,y bounds
  xlab = "Ventral Striatum DRD2 BPND", ylab = "prop(Low Effort)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 20)  # Add correlation coefficient
vstr_effort
```

Effort (Ln(k+1))
```{r}
vstr_effort <- ggscatter(data, x = "accumbens_pvc", y = "effort_ln_k1",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(10,60), ylim=c(0,2.5),                             #x,y bounds
  xlab = "Ventral Striatum DRD2 BPND", ylab = "Effort (Ln(k+1))",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 20)  # Add correlation coefficient
vstr_effort
```

####Age * Putamen Interaction: Time Discounting
Chose Sooner
```{r}
put_time <- ggscatter(data, x = "putamen_pvc", y = "chosesnr",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(20,50), ylim=c(0,1),                             #x,y bounds
  xlab = "Putamen DRD2 BPND", ylab = "prop(Sooner)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 45)  # Add correlation coefficient
put_time
```

####Age * Amygdala Interaction: Probability Discounting
Chose High Probability
```{r}
amyg_prob <- ggscatter(data, x = "amygdala_pvc", y = "prob_ln_k1",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(1,6), ylim=c(0,3),                             #x,y bounds
  xlab = "Amygdala DRD2 BPND", ylab = "Probability Ln(k+1)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 1.5)  # Add correlation coefficient
amyg_prob
```

####Age * Amygdala Interaction: Effort Discounting
Effort(Ln(k+1))
```{r}
amyg_effort <- ggscatter(data, x = "amygdala_pvc", y = "effort_ln_k1",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(1,6), ylim=c(0,3),                             #x,y bounds
  xlab = "Amygdala DRD2 BPND", ylab = "Effort Ln(k+1)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 1.5)  # Add correlation coefficient
amyg_effort
```

####Age * Hippocampus Interaction: Effort Discounting
Effort(Ln(k+1))
```{r}
hipp_effort <- ggscatter(data, x = "hippocampus_pvc", y = "effort_ln_k1",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(0,4), ylim=c(0,3),                             #x,y bounds
  xlab = "Hippocampus DRD2 BPND", ylab = "Effort Ln(k+1)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 0.5)  # Add correlation coefficient
hipp_effort
```

####Age * Thalamus Interaction: Effort Discounting
Effort(Ln(k+1))
```{r}
thal_effort <- ggscatter(data, x = "thalamus_pvc", y = "effort_ln_k1",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(1,5), ylim=c(0,3),                             #x,y bounds
  xlab = "Thalamus DRD2 BPND", ylab = "Effort Ln(k+1)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 4)  # Add correlation coefficient
thal_effort
```

####Age * ACC Interaction: Probability Discounting
Chose High Probability
```{r}
acc_prob <- ggscatter(data, x = "acc_pvc", y = "prob_ln_k1",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(0,3), ylim=c(0,3),                             #x,y bounds
  xlab = "ACC DRD2 BPND", ylab = "Probability Ln(k+1)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 2.5)  # Add correlation coefficient
acc_prob
```

####Age * ACC Interaction: Effort Discounting
Effort(Ln(k+1))
```{r}
acc_effort <- ggscatter(data, x = "acc_pvc", y = "effort_ln_k1",
  add = "reg.line",                                       # Add regression line
  conf.int = TRUE,                                        # Add confidence interval
  color = "age_tertiary_split", palette = "jco",               # Color by age groups
  xlim=c(0,3), ylim=c(0,2),                             #x,y bounds
  xlab = "ACC DRD2 BPND", ylab = "Effort Ln(k+1)",  #labels
  legend.title = "Age Group"
  )+
  stat_cor(aes(color = data$age_tertiary_split), label.x = 1.5)  # Add correlation coefficient
acc_effort
```
